---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# eltoolkit

<!-- badges: start -->
<!-- badges: end -->

The goal of eltoolkit is to provide its users with helpers functions that would make their lives easier.

## Installation

You can install the development version of eltoolkit from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("erwinlares/eltoolkit")
```

## Examples

### How to use the `rac_csv()` function

This is how you read a csv file into your environment *and* clean the variable names in one fell swoop.

```{r example}
library(eltoolkit)
data <- rac_csv("data.csv")
```


### How to use the `create_project2` function

To create a new project with a basic template that includes `data`, `images`, `plots`, and `scripts`. This will create a new project, place it as a subdirectory of `Desktop`, and name it "myproject". It will also create a new R session and open the project. 

```{r example2}
library(eltoolkit)
create_project2("~/Desktop/myproject")
```


`create_project2()` support passing additional character string arguments. When you do that, it will create additional folders with the names of the arguments. You may pass as many additional argument and you need. For instance, to create a `reports` folder, run the code below.

```{r example3}
library(eltoolkit)
create_project2("~/Desktop/myproject", "reports")
```
