---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# eltoolkit

<!-- badges: start -->
<!-- badges: end -->

The goal of eltoolkit is to provide its users with helpers functions that would make their lives easier.

## Installation

You can install the development version of eltoolkit from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("erwinlares/eltoolkit")
```

## Examples

### How to use the `rac_csv()` function

Use `rac_csv` to read a csv file into your environment *and* clean the variable names in one fell swoop. `rac` stands for "read and clean". 

```{r example}
library(eltoolkit)
data <- rac_csv("data.csv")
```


### How to use the `create_project2` function

Use `create_project2()` to create a new project with a basic template that includes `data`, `images`, `plots`, and `scripts`. The code below will create a new project, place it as a subdirectory of `Desktop`, and name it "myproject". It will then create a new R session and open the project. 

```{r example2}
library(eltoolkit)
create_project2("~/Desktop/myproject")
```


`create_project2()` supports passing additional arguments as character strings. When you do that, `create_project2()` will create additional folders with the names of the arguments. You may pass as many additional argument as you need. For instance, to create a `reports` folder, run the code below.

```{r example3}
library(eltoolkit)
create_project2("~/Desktop/myproject", "reports")
```
